Test SUSIE (L=3) for regions near genes (500kb flanking)

### 2020-06-24 analysis/index.Rmd
susie more examples
susie examples

  * [Using UKbiobank data (chr22), fusion weights YFS](simulation-susie-ukbchr22.html)

>>>>

  * [Using UKbiobank data (chr22), fusion weights YFS,  SUSIE `L=1`](simulation-susie-ukbchr22.html)
  * [Using UKbiobank data (chr22), fusion weights YFS, SUSIE `L=2`](simulation-susie-ukbchr22-L=2.html)
  * [Using UKbiobank data (chr22), fusion weights YFS,  SUSIE `L=3`](simulation-susie-ukbchr22-L=3.html)

  * [Using UKbiobank data (chr22), fusion weights Adipose, `L=1`](simulation-susie-ukbchr22-gtex.adipose.html)

### 2020-06-24 analysis/simulation-susie-ukbchr22-L=2.Rmd
susie examples

---
title: "Test SUSIE for regions near genes (500kb flanking)"
output: html_document
---

@@

```{r sim 1 3, out.width = "98%", out.height="95%", eval =T}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag, "-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

name <- "MCM5"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

[Zoomlocus view for CBX7 region](https://users.rcc.uchicago.edu/~simingz/chr22_39026778-40048655.pdf)
```{r zoomlocus, out.width = "85%", include = F}
file.copy("/home/simingz/causalTWAS/simulations/simulation_ashtest_20200503/snp_200622_CBX7/chr22_39026778-40048655.pdf", "~/public_html/chr22_39026778-40048655.pdf")
```

@@

```{r sim 5 1, out.width = "98%", out.height="95%"}
name <- "CRELD2"
susieres <- paste0(outputdir, tag, ".", tag2, "-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

>>>>

---
title: "Test SUSIE (L=2) for regions near genes (500kb flanking)"
output: html_document
---

@@

```{r sim 1 3, out.width = "98%", out.height="95%", eval =T}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag, ".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

name <- "MCM5"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

[Zoomlocus view for this region](https://users.rcc.uchicago.edu/~simingz/chr22_39026778-40048655.pdf)
```{r zoomlocus, out.width = "85%", include = F}
file.copy("/home/simingz/causalTWAS/simulations/simulation_ashtest_20200503/snp_200622_CBX7/chr22_39026778-40048655.pdf", "~/public_html/chr22_39026778-40048655.pdf")
```

@@

```{r sim 5 1, out.width = "98%", out.height="95%"}
name <- "CRELD2"
susieres <- paste0(outputdir, tag, ".", tag2, ".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

### 2020-06-24 analysis/simulation-susie-ukbchr22-L=3.Rmd
susie examples

---
title: "Test SUSIE (L=2) for regions near genes (500kb flanking)"
output: html_document
---

@@

```{r sim 1 3, out.width = "98%", out.height="95%", eval =T}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag, ".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

name <- "MCM5"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

```{r sim 5 1, out.width = "98%", out.height="95%"}
name <- "CRELD2"
susieres <- paste0(outputdir, tag, ".", tag2, ".L2-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

>>>>

---
title: "Test SUSIE (L=3) for regions near genes (500kb flanking)"
output: html_document
---

@@

```{r sim 1 3, out.width = "98%", out.height="95%", eval =T}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag, ".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

name <- "MCM5"
susieres <- paste0(outputdir, susietag,".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

```{r sim 5 1, out.width = "98%", out.height="95%"}
name <- "CRELD2"
susieres <- paste0(outputdir, tag, ".", tag2, ".L3-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```
